---
title       : Interactive linear model comparison
subtitle    : Illustration with the mtcars dataset
author      : Laurent Franckx 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]         # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---


## Introduction

- app addresses  determinants of  miles per callon (MPG) of passenger cars 
- mtcars dataset contains 32 observations on 11 variables
- app allows user to compare two different linear model specifications with different regressors
- user can fine tune displayed information

--- .class #id 


## Output info of the app

- default summary for the dataset

- histogram for chosen variable

- default summary tables for each model

- model diagnostics  to identify influential observations.

- plots to identify outliers and influential observations 

- ANOVA table comparing the two models if embedded 

--- .class #id 


## Illustration

- The complete app can be found at:

https://lfranckx.shinyapps.io/course_shiny_project/

- Illustration of the choice possibilities for the histogram:

- Next slide: Illustration of regressor choice and model summary:



```{r opts.label = 'shiny', echo=FALSE}
slidifyUI(
  sidebarPanel(
        fluidRow(
          h4("Show histogram for one selected variable:"),
          selectInput("histo_var", 
                      label = "Chosen variable:", 
                      list("mpg" = "mpg", "cyl" = "cyl", "disp" = "disp", "hp"= "hp", "drat" = "drat", "wt" = "wt", 
                           "qsec" = "qsec", "vs" = "vs","am"= "am", 
                           "gear"= "gear", "carb"= "carb"),
                      selected = "cyl"
          ),
          numericInput("bin", 
                       label = "Maximal number of bins:", 
                       value = 10)
          )
    ),
  mainPanel(
    h4('The histogram of the chosen variable is:'),
    plotOutput("plothisto")
  )
)

```

 
--- .class #id 
##Test

- this is some test text

--- .class #id 


```{r opts.label = 'shiny', echo=TRUE}
slidifyUI(
  sidebarPanel(
      h3("Parameters for the  model:"),
      checkboxGroupInput("Var_choice_1", 
                       label = h4("Regressors to include in first model:"), 
                       list("cyl" = "cyl", "disp" = "disp", "hp"= "hp", "drat" = "drat", "wt" = "wt", 
                            "qsec" = "qsec", "vs" = "vs","am"= "am", 
                            "gear"= "gear", "carb"= "carb"),
                       selected = "cyl")

    ),
  mainPanel(
    h4('The first model results are:'),
     verbatimTextOutput("modres1")
  )
)

```

